Safety Cases for Software Product Lines: Terminology and Example

### 2017-12-09 doc/SafetyCases/SafetyCasesPL.tex
safety cases presentation

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

\lstset{
     basicstyle=\ttfamily,
     keywordstyle=\color{blue}\ttfamily,
     stringstyle=\color{red}\ttfamily,
     commentstyle=\color{green}\ttfamily,
     morecomment=[l][\color{magenta}]{\#},
     numbers=left, 
     tabsize=2,
     captionpos=b, 
     frame=shadowbox,
     language=Java,
     morekeywords={if, endif, defined, refines, core, delta, modifies, remove, add, when}
}

>>>>

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

\lstset{
     basicstyle=\ttfamily,
     keywordstyle=\color{blue}\ttfamily,
     stringstyle=\color{red}\ttfamily,
     commentstyle=\color{Gray}\ttfamily,
     morecomment=[l][\color{magenta}]{\#},
     numbers=left, 
     tabsize=2,
     captionpos=b, 
     frame=shadowbox,
     language=Java,
     morekeywords={if, endif, defined, refines, core, delta, modifies, remove, add, when}
}
